Expectations, Outcomes, and Challenges \\ of Modern Code Review

### 2013-01-10 reviews.tex
revised review 2 and 3

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{review} {}

@@

\begin{review}{}

@@

\item[p.2] Please describe the initial in-field observations

\item[p.3] was there a Hawthorne effect to the ``thought aloud'' portion of the work?

\item[p.4] top left column - please show a sample card?

\item[p.4] top left - is there not possible bias from the first author sorting the
cards to form initial themes?

\item[p.4] middle of left column - how time consuming were the card sorts?

@@

There are some typos and minor grammatical issues - a thorough proofread of the
paper will remedy this

p. 9 need text under section VII header

@@

\begin{review}{}

@@

The paper makes great use of triangulation, i.e., seeking additional evidence
to support or refute a tentative interpretation. One of the most interesting
was the observation, from the interviews and comments, that usually only
superficial bugs were found, and another observation that unfamiliar code was
very hard to understand. In the survey of developers, they asked for each of
the inspection outcomes (e.g., finding bugs, learning about the code, improving
the code) how much code understanding was required (rated on a scale from
"none" to "complete"). Interestingly, "finding defects" came out as requiring
the greatest level of understanding, and along with "alternative solutions"
were so far above the others, that they seem qualitatively very different.
Other outcomes one might expect to be similar, such as "code improvement" were
far lower. This finding not only reinforces the earlier results about finding
only superficial bugs and understanding being the most difficult part of the
inspection, it suggests an interesting relationship between the two.

This is an important paper. It provides convincing evidence that inspections
are important, but not for the reasons we thought. In fact, under many
conditions, they are not terribly useful for finding bugs, but they accomplish
many other important purposes. As the authors point out, tools and processes
are optimized around those things that inspections are not very good at, and
they neglect important things like providing assistance for understanding the
code, creating a sense of shared ownership, and transferring knowledge. I think
this paper will change how the field thinks about inspections and what we need
to support them. In fact, it has implications beyond inspections, for example,
the about the potential value of "transparent" environments, such as GitHub,
where all coding is done out in the open, and for pair programming that in
practice can be very close to lightweight inspections, and serves many of the
same purposes.

As an aside, the paper also introduces some interesting analysis techniques.
Open sorting is an interesting variation on the standard qualitative technique
of open coding, and the way they used the affinity diagram - as a technique to
find order in the categories they derived from open coding - is an interesting
way to carry out axial coding. It might be helpful to readers to connect these
techniques with the classical qualitative methods works such as:

@@

\item[p.1] explorative --$>$ exploratory

\item[p.3]: we contacted 100 random candidates - I think you mean they were selected
randomly. The candidates might bristle at being called random . . .

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{review} {The Bad}

@@

\begin{review}{The Ugly}

@@

\item[p.2] Please \hl{describe the initial in-field observations}.

\item[p.3] was there a \hl{Hawthorne effect to the ``thought aloud'' portion} of the work?

\item[p.4] top left column - please \hl{show a sample card}?

\item[p.4] top left - is there not possible \hl{bias from the first author sorting the
cards} to form initial themes?

\item[p.4] middle of left column - \hl{how time consuming were the card sorts}?

@@

\item[pp.] There are some typos and minor grammatical issues - a thorough proofread of the
paper will remedy this

\item[p.9] need text under section VII header

@@

\begin{review}{The Good}

@@

The paper makes great use of triangulation, i.e., seeking additional evidence
to support or refute a tentative interpretation. One of the most interesting
was the observation, from the interviews and comments, that usually only
superficial bugs were found, and another observation that unfamiliar code was
very hard to understand. In the survey of developers, they asked for each of
the inspection outcomes (e.g., finding bugs, learning about the code, improving
the code) how much code understanding was required (rated on a scale from
``none'' to ``complete''). Interestingly, ``finding defects'' came out as requiring
the greatest level of understanding, and along with ``alternative solutions''
were so far above the others, that they seem qualitatively very different.
Other outcomes one might expect to be similar, such as ``code improvement'' were
far lower. This finding not only reinforces the earlier results about finding
only superficial bugs and understanding being the most difficult part of the
inspection, it suggests an interesting relationship between the two.

This is an important paper. It provides convincing evidence that inspections
are important, but not for the reasons we thought. In fact, under many
conditions, they are not terribly useful for finding bugs, but they accomplish
many other important purposes. As the authors point out, tools and processes
are optimized around those things that inspections are not very good at, and
they neglect important things like providing assistance for understanding the
code, creating a sense of shared ownership, and transferring knowledge. I think
this paper will change how the field thinks about inspections and what we need
to support them. In fact, it has implications beyond inspections, for example,
the about the potential value of ``transparent'' environments, such as GitHub,
where all coding is done out in the open, and for pair programming that in
practice can be very close to lightweight inspections, and serves many of the
same purposes.

As an aside, the paper also introduces some interesting analysis techniques.
Open sorting is an interesting variation on the standard qualitative technique
of open coding, and the way they used the affinity diagram - as a technique to
find order in the categories they derived from open coding - is an interesting
way to carry out axial coding. \hl{It might be helpful to readers to connect these
techniques with the classical qualitative methods works} such as:

@@

@@

\AB{I am not mentioning the two ``nits'' already fixed}
